---
title: "10x Genomics scATAC-seq QC"
author: 
 - Lucas Graybuck
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    self_contained: true
params:
  in_dir: NULL
  batch_id: NULL
  out_dir: NULL
---

<a id="contents"></a>

## Contents

#### [Data Processing](#data_processing)
- [Session Preparation](#session_preparation)
- [Assemble Metadata](#assemble_meta)

#### [QC Metrics](#qc_stats)
- [Cell Barcode QC](#barcode_stats)
- [Fragment Metrics](#fragment_stats)
  - [Unique Fragments](#fragment_stats_unique)
  - [Mito. Fragments](#fragment_stats_mito)
  - [FRIP](#fragment_stats_frip)
  - [FRITSS](#fragment_stats_fritss)
  - [Fraction in ENCODE/Altius Index](#fragment_stats_fralt)
- [Saturation Metrics](#saturation_stats)
- [Fragment Widths](#width_stats)

[Write QC JSON](#json_out)

#### [Session Info](#session_info)

<a id="data_processing"></a>

## Data Processing

<a id="session_preparation"></a>

### Session Preparation

#### Load libraries:
```{r Load Libraries}
start_time <- Sys.time()

quiet_library <- function(...) {
  suppressPackageStartupMessages(library(...))
}
quiet_library(data.table)
quiet_library(H5weaver)
quiet_library(ggplot2)
quiet_library(cowplot)
quiet_library(jsonlite)
quiet_library(purrr)
options(stringsAsFactors = FALSE)
```

Declaring start
```{r Declare start}
stm("Starting Batch Report")
```

#### Argument parsing
```{r Parse arguments}
if(is.null(params$in_dir)) {
  in_dir <- system.file("testdata/batch_qc", package = "ATAComb")
  batch_id <- "X000"
  out_dir <- tempdir()
} else {
  in_dir <- params$in_dir
  batch_id <- params$batch_id
  out_dir <- params$out_dir
}

stm(paste0("IN  results dir      : ", in_dir))
stm(paste0("IN  BatchID          : ", batch_id))
stm(paste0("OUT Directory        : ", out_dir))
```

#### Input Parameters
```{r Print Arguments}
print(c(
  paste0("IN  results dir      : ", in_dir),
  paste0("IN  BatchID          : ", batch_id),
  paste0("OUT H5 directory     : ", out_dir)
))
```

#### Check Input Files
```{r Check Inputs}
if(!dir.exists(in_dir)) {
  stm(paste("ERROR: Cannot find IN results dir:", in_dir))
  stop()
}
if(!dir.exists(out_dir)) {
  stm(paste("Creating output directory:", out_dir))
  dir.create(out_dir)
}
out_prefix <- file.path(out_dir, paste0(batch_id, "_"))
```

#### Check available files

Unfiltered metadata
```{r}
meta_files <- list.files(in_dir, 
                         pattern = "_all_metadata.csv.gz$",
                         full.names = TRUE)
if(length(meta_files) == 0) {
  stop("Can't find unfiltered metadata files. Check input directory for *_all_metadata.csv.gz files.")
}

meta_list <- map(meta_files, fread)
sample_names <- sub(".+/","",sub("_all_metadata.csv.gz","",meta_files))
names(meta_list) <- sample_names
```

Filtered metadata
```{r}
filt_meta_files <- list.files(in_dir, 
                         pattern = "_filtered_metadata.csv.gz$",
                         full.names = TRUE)

if(length(filt_meta_files) < length(meta_files)) {
  stop("Can't find filtered metadata files. Check input directory for *_filtered_metadata.csv.gz files.")
} else if(length(filt_meta_files) > length(meta_files)) {
  stop("Can't find all metadata files. Check input directory for *_all_metadata.csv.gz files.")
}

filt_meta_list <- map(filt_meta_files, fread)
names(filt_meta_list) <- sub(".+/","",sub("_filtered_metadata.csv.gz","",filt_meta_files))
filt_meta_list <- filt_meta_list[sample_names]
```

Saturation projections
```{r}
sat_files <- list.files(in_dir,
                        pattern = "_saturation_projection.csv.gz$",
                        full.names = TRUE)

if(length(sat_files) < length(meta_files)) {
  stop("Can't find all saturation files. Check input directory for *_saturation_projection.csv.gz files.")
} else if(length(sat_files) > length(meta_files)) {
  stop("Can't find all metadata files. Check input directory for *_all_metadata.csv.gz files.")
}

names(sat_files) <- sub(".+/","",sub("_saturation_projection.csv.gz","",sat_files))
sat_files <- sat_files[sample_names]

sat_list <- map(sat_files, fread)
```

Fragment widths
```{r}
width_files <- list.files(in_dir,
                          pattern = "_fragment_width_summary.csv.gz",
                          full.names = TRUE)

if(length(width_files) < length(meta_files)) {
  stop("Can't find all fragment width files. Check input directory for *_fragment_width_summary.csv.gz files.")
} else if(length(sat_files) > length(meta_files)) {
  stop("Can't find all metadata files. Check input directory for *_all_metadata.csv.gz files.")
}

names(width_files) <- sub(".+/","",sub("_fragment_width_summary.csv.gz","",width_files))
width_files <- width_files[sample_names]

width_list <- map(width_files, fread)
```

[Return to Contents](#contents)

<a id="assemble_meta"></a>

#### Combine metadata
```{r}
filtered_meta <- do.call(rbind, filt_meta_list)
meta <- do.call(rbind, meta_list)

cutoffs <- list(altius_frac = 0.5,
                tss_frac = 0.2,
                peaks_frac = 0.2)

meta$pass_fail <- "pass"
for(i in seq_along(cutoffs)) {
  cut_name <- names(cutoffs)[i]
  cut_val <- cutoffs[[i]]
  cut_logic <- meta[[cut_name]] <= cut_val
  meta$pass_fail[cut_logic] <- "fail"
}

meta$filtered <- meta$barcodes %in% filtered_meta$barcodes
meta$mito_frac <- meta$n_mito / meta$n_fragments
```

#### Filter metadata based on cutoffs
```{r}
stm("Filtering based on QC cutoffs")

filtered_meta <- meta
for(i in seq_along(cutoffs)) {
  cut_name <- names(cutoffs)[i]
  cut_val <- cutoffs[[i]]
  filtered_meta <- filtered_meta[filtered_meta[[cut_name]] > cut_val]
  filtered_meta <- filtered_meta[filtered_meta$filtered,]
}
```

Set up global metadata for reporting
```{r}
meta$barcode_category <- "fail_qc"
meta$barcode_category[!meta$filtered & meta$pass_fail == "pass"] <- "pass_doublet"
meta$barcode_category[meta$filtered & meta$pass_fail == "pass"] <- "pass_singlet"
```

[Return to Contents](#contents)

<a id="qc_stats"></a>

### QC Stats

```{r}
qc_list <- list(report_type = "atac_batch_qc",
                report_datetime = as.character(start_time),
                report_uuid = ids::uuid(use_time = TRUE),
                package = "ATAComb",
                package_version = sessionInfo()$otherPkgs$ATAComb$Version,
                batch_id = sub("_.+","",sample_names[1]))

out_json <- paste0(out_prefix, "atac_batch_qc_metrics.json")
```

[Return to Contents](#contents)

<a id="barcode_stats"></a>

#### Barcode QC Stats
```{r}
barcode_counts <- meta[,.(n_barcodes = nrow(.SD),
                            n_pass_qc = sum(.SD$pass_fail == "pass"),
                            n_fail_qc = sum(.SD$pass_fail == "fail"),
                            percent_fail = round(sum(.SD$pass_fail == "fail")/nrow(.SD)*100,2),
                            pass_singlets = sum(.SD$barcode_category == "pass_singlet"),
                            pass_doublets = sum(.SD$barcode_category == "pass_doublet"),
                            percent_doublets = round(sum(.SD$barcode_category == "pass_doublet")/sum(.SD$pass_fail == "pass")*100,2)),
                         well_id]

qc_list$barcode_stats <- as.list(barcode_counts)

qc_table(barcode_counts)
```

```{r}
qc_stacked_barplot(meta,
                   category_x = "well_id",
                   name_x = "Well ID",
                   category_y = "barcode_category",
                   category_name = "Barcode Category",
                   as_fraction = TRUE)
```

```{r}
qc_aligned_barplot(meta,
                   category_x = "well_id",
                   name_x = "Well ID",
                   category_y = "barcode_category",
                   category_name = "Barcode Category")
```

[Return to Contents](#contents)

<a id="fragment_stats"></a>

#### Fragment QC stats

```{r}
fragment_stats <- filtered_meta[,.(n_singlets = nrow(.SD[.SD$filtered]),
                                   med_raw_frag = round(median(n_fragments),0),
                                   med_raw_perc_mito = round(median(mito_frac)*100,4),
                                   med_unique_frag = round(median(n_unique),0),
                                   med_unique_fritss = round(median(tss_frac),4),
                                   med_unique_frip = round(median(peaks_frac),4),
                                   med_unique_encode = round(median(altius_frac),4)
                                   ),
                                well_id]

qc_list$fragment_stats <- as.list(fragment_stats)

qc_table(fragment_stats)
```

[Return to Contents](#contents)

<a id="fragment_stats_unique"></a>

#### Unique Fragments per Cell
```{r}
category_reads_violins <- qc_violin_plot(meta,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "n_unique",
                                         name_y = "Unique Fragments",
                                         fill = "dodgerblue")
well_reads_violins <- qc_violin_plot(filtered_meta,
                                     category_x = "well_id",
                                     name_x = "Well ID",
                                     column_y = "n_unique",
                                     name_y = "Unique Fragments (Singlets)",
                                     fill = "dodgerblue")

reads_violin_list <- list(category_reads_violins, 
                          well_reads_violins)

plot_grid(plotlist = reads_violin_list,
          ncol = 2, rel_widths = c(1, 3),
          nrow = 1, align = "h")
```

[Return to Contents](#contents)

<a id="fragment_stats_mito"></a>

#### Fraction of Raw Reads in Mitochondria per Cell
```{r}
category_mito_violins <- qc_violin_plot(meta,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "mito_frac",
                                         name_y = "Fraction Mitochondrial",
                                         fill = "darkgreen",
                                        log_y = FALSE)
well_mito_violins <- qc_violin_plot(filtered_meta,
                                     category_x = "well_id",
                                     name_x = "Well ID",
                                     column_y = "mito_frac",
                                     name_y = "Fraction Mito. (Singlets)",
                                     fill = "darkgreen",
                                    log_y = FALSE)

mito_violin_list <- list(category_mito_violins, 
                          well_mito_violins)

plot_grid(plotlist = mito_violin_list,
          ncol = 2, rel_widths = c(1, 3),
          nrow = 1, align = "h")
```

[Return to Contents](#contents)

<a id="fragment_stats_frip"></a>

#### Fraction of Reads in Peaks per Cell
```{r}
category_frip_violins <- qc_violin_plot(meta,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "peaks_frac",
                                         name_y = "FRIP",
                                         fill = "orangered",
                                        log_y = FALSE)
well_frip_violins <- qc_violin_plot(filtered_meta,
                                     category_x = "well_id",
                                     name_x = "Well ID",
                                     column_y = "peaks_frac",
                                     name_y = "FRIP (Singlets)",
                                     fill = "orangered",
                                    log_y = FALSE)

frip_violin_list <- list(category_frip_violins, 
                          well_frip_violins)

plot_grid(plotlist = frip_violin_list,
          ncol = 2, rel_widths = c(1, 3),
          nrow = 1, align = "h")
```

#### Reads vs peaks_frac scatter
```{r fig.width=12, fig.height = 6}
well_ids <- unique(filtered_meta$well_id)
n_wells <- length(well_ids)

qc_scatter_list <- map(well_ids,
                       function(well_id) {
                         well_meta <- filtered_meta[filtered_meta$well_id == well_id,]
                         qc_scatter_plot(well_meta,
                                         column_x = "n_unique",
                                         name_x = "N Unique Fragments per Cell",
                                         column_y = "peaks_frac",
                                         name_y = "Frac Fragments in Peaks (peaks_frac)",
                                         log_x = TRUE, log_y = FALSE, frac_y = TRUE,
                                         show_targets = FALSE,
                                         color = "orangered") +
                           geom_vline(aes(xintercept = 2.5e3), linetype = "dashed", size = 0.2) +
                           geom_hline(aes(yintercept = cutoffs$peaks_frac), linetype = "dashed", size = 0.2)
                       })

plot_grid(plotlist = qc_scatter_list,
          ncol = min(n_wells, 4))
```

[Return to Contents](#contents)

<a id="fragment_stats_fritss"></a>

#### Fraction of Reads in TSS (+/- 2kb) per Cell
```{r}
category_fritss_violins <- qc_violin_plot(meta,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "tss_frac",
                                         name_y = "FRITSS",
                                         fill = "mediumorchid3",
                                        log_y = FALSE)
well_fritss_violins <- qc_violin_plot(filtered_meta,
                                     category_x = "well_id",
                                     name_x = "Well ID",
                                     column_y = "tss_frac",
                                     name_y = "FRITSS (Singlets)",
                                     fill = "mediumorchid3",
                                    log_y = FALSE)

fritss_violin_list <- list(category_fritss_violins, 
                          well_fritss_violins)

plot_grid(plotlist = fritss_violin_list,
          ncol = 2, rel_widths = c(1, 3),
          nrow = 1, align = "h")
```

#### Reads vs tss_frac scatter
```{r fig.width=12, fig.height = 6}
well_ids <- unique(filtered_meta$well_id)
n_wells <- length(well_ids)

qc_scatter_list <- map(well_ids,
                       function(well_id) {
                         well_meta <- filtered_meta[filtered_meta$well_id == well_id,]
                         qc_scatter_plot(well_meta,
                                         column_x = "n_unique",
                                         name_x = "N Unique Fragments per Cell",
                                         column_y = "tss_frac",
                                         name_y = "Frac Fragments in TSS (tss_frac)",
                                         log_x = TRUE, log_y = FALSE, frac_y = TRUE,
                                         show_targets = FALSE,
                                         color = "mediumorchid3") +
                           geom_vline(aes(xintercept = 2.5e3), linetype = "dashed", size = 0.2) +
                           geom_hline(aes(yintercept = cutoffs$tss_frac), linetype = "dashed", size = 0.2)
                       })

plot_grid(plotlist = qc_scatter_list,
          ncol = min(n_wells, 4))
```

[Return to Contents](#contents)

<a id="fragment_stats_fralt"></a>

#### Fraction of Reads in ENCODE/Altius Index per Cell
```{r}
category_enc_violins <- qc_violin_plot(meta,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "altius_frac",
                                         name_y = "FRIENCODE",
                                         fill = "darkred",
                                        log_y = FALSE)
well_enc_violins <- qc_violin_plot(filtered_meta,
                                     category_x = "well_id",
                                     name_x = "Well ID",
                                     column_y = "altius_frac",
                                     name_y = "FRIENCODE (Singlets)",
                                     fill = "darkred",
                                    log_y = FALSE)

enc_violin_list <- list(category_enc_violins, 
                          well_enc_violins)

plot_grid(plotlist = enc_violin_list,
          ncol = 2, rel_widths = c(1, 3),
          nrow = 1, align = "h")
```

#### Reads vs altius_frac scatter
```{r fig.width=12, fig.height = 6}
well_ids <- unique(filtered_meta$well_id)
n_wells <- length(well_ids)

qc_scatter_list <- map(well_ids,
                       function(well_id) {
                         well_meta <- filtered_meta[filtered_meta$well_id == well_id,]
                         qc_scatter_plot(well_meta,
                                         column_x = "n_unique",
                                         name_x = "N Unique Fragments per Cell",
                                         column_y = "altius_frac",
                                         name_y = "Frac Fragments in Altius (altius_frac)",
                                         log_x = TRUE, log_y = FALSE, frac_y = TRUE,
                                         show_targets = FALSE,
                                         color = "darkred") +
                           geom_vline(aes(xintercept = 2.5e3), linetype = "dashed", size = 0.2) +
                           geom_hline(aes(yintercept = cutoffs$altius_frac), linetype = "dashed", size = 0.2)
                       })

plot_grid(plotlist = qc_scatter_list,
          ncol = min(n_wells, 4))
```

[Return to Contents](#contents)

<a id="saturation_stats"></a>

#### Saturation metrics
```{r}
all_sat <- map_dfr(1:length(sat_list),
                   function(x) {
                     sat <- sat_list[[x]]
                     sat$well_id <- sub(".+_","",names(sat_list)[x])
                     sat
                   })
```

#### Saturation cutoffs
```{r}
all_sat <- as.data.table(all_sat)
sat_cutoffs <- all_sat[,.(M_raw = max(.SD$M_raw_reads[.SD$type == "actual"]),
                          M_umis = max(.SD$M_umis[.SD$type == "actual"]),
                          M_signal = max(.SD$M_signal_umis[.SD$type == "actual"]),
                          M_raw_2x_UMIs = .SD$M_raw_reads[which.min(abs(.SD$ratio - 2))[1]],
                          M_raw_4x_UMIs = .SD$M_raw_reads[which.min(abs(.SD$ratio - 4))[1]],
                          M_raw_2x_signal = .SD$M_raw_reads[which.min(abs(.SD$signal_ratio - 2))[1]],
                          M_raw_4x_signal = .SD$M_raw_reads[which.min(abs(.SD$signal_ratio - 4))[1]],
                          M_raw_8x_signal = .SD$M_raw_reads[which.min(abs(.SD$signal_ratio - 8))[1]]),
                       well_id]

qc_list$saturation_stats <- as.list(sat_cutoffs)

qc_table(sat_cutoffs)
```

#### Saturation of Unique Fragments
```{r fig.width=12, fig.height = 6}
reference_projections <- fread(system.file("reference/saturation/reference_projections.csv",
                                           package = "ATAComb"))
reference_projections$dataset <- paste0("ref_",reference_projections$dataset)

umi_saturation_plot <- ggplot() +
  geom_line(data = reference_projections,
            aes(x = n_raw_reads,
                y = expected_umis,
                group = dataset,
                color = dataset)) +
  geom_line(data = all_sat,
            aes(x = n_raw_reads,
                y = expected_umis,
                group = well_id,
                color = type),
            size = 1)  +
  scale_color_brewer("Data Type",
                     type = "qual",
                     palette = 2) +
  scale_x_continuous("N Raw Reads (millions)",
                     expand = c(0,0),
                     limits = c(0, 1.5e9),
                     breaks = seq(0, 1.5e9, by = 2.5e8),
                     labels = seq(0, 1500, by = 250)) +
  scale_y_continuous("N Unique Fragments (millions)", 
                     expand = c(0,0),
                     limits = c(0, 5e8),
                     breaks = seq(0, 5e8, by = 1e8),
                     labels = seq(0, 500, by = 100)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  facet_wrap(facets = vars(well_id), ncol = 4) +
  ggtitle("Saturation of All Unique Fragments")

umi_saturation_plot
```

#### Saturation of Signal Fragments
Signal fragments are reads in Altius Index regions in barcodes passing QC
```{r fig.width=12, fig.height = 6}
signal_saturation_plot <- ggplot() +
  geom_line(data = reference_projections,
            aes(x = n_raw_reads,
                y = signal_umis,
                group = dataset,
                color = dataset)) +
  geom_line(data = all_sat,
            aes(x = n_raw_reads,
                y = signal_umis,
                group = well_id,
                color = type),
            size = 1)  +
  scale_color_brewer("Data Type",
                     type = "qual",
                     palette = 2) +
  scale_x_continuous("N Raw Reads (millions)",
                     expand = c(0,0),
                     limits = c(0, 1.5e9),
                     breaks = seq(0, 1.5e9, by = 2.5e8),
                     labels = seq(0, 1500, by = 250)) +
  scale_y_continuous("N Signal Fragments (millions)", 
                     expand = c(0,0),
                     limits = c(0, 2e8),
                     breaks = seq(0, 2e8, by = 2e7),
                     labels = seq(0, 200, by = 20)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  facet_wrap(facets = vars(well_id), ncol = 4) +
  ggtitle("Saturation of Signal Fragments")

signal_saturation_plot
```

[Return to Contents](#contents)

<a id="width_stats"></a>

#### Fragment Width Distributions
```{r fig.width=12, fig.height = 6}
frag_widths <- map_dfr(1:length(width_list),
                   function(x) {
                     fw <- width_list[[x]]
                     fw$well_id <- sub(".+_","",names(width_list)[x])
                     fw
                   })

frag_widths <- frag_widths[width <= 750]

ggplot(data = frag_widths) +
  geom_line(aes(x = width,
                y = frac,
                group = pass_fail,
                color = pass_fail),
            size = 1) +
  xlim(0, 750) +
  facet_wrap(vars(well_id), ncol = 2) +
  theme_bw()
```

[Return to Contents](#contents)

<a id="json_out"></a>

### Write QC JSON

```{r Save QC JSON}
stm(paste0("Writing JSON to ",out_json))

qc_list_json <- jsonlite::toJSON(qc_list,
                                 auto_unbox = TRUE,
                                 pretty = TRUE)

writeLines(qc_list_json,
           out_json)
```

[Return to Contents](#contents)

<a id="session_info"></a>

## Session Information

```{r Session Info}
sessionInfo()
```

Total time elapsed
```{r Show Time}
end_time <- Sys.time()
diff_time <- end_time - start_time
time_message <- paste0("Elapsed Time: ", 
                       round(diff_time, 3),
                       " ", units(diff_time))
print(time_message)
stm(time_message)
stm("10x ATAC Batch QC Report complete.")
```

[Return to Contents](#contents)
